Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-07-20 doc/PRF2022/PRF_main.tex
yny 0720 7

The boundary condition on JP can be put into three categories: min$(g) >0$, min$(g) =0$, and min$(g) <0$. Without loss of generality, 
these three categories correspond to three characteristic values of $b$ in \eqref{eq:bc-type}: $b=2$, $b=1$ and $b=0$, respectively. 
%
To see the effect of the shift parameter $b$, we simulate the dynamics of
198 particles and 60 particles in a quiescent flow as shown in Figure~\ref{fig:relax}.
Three distinct configurations emerge:
(i) bilayers for $b = 1$, 
(ii) multilamellar for $b = 2$, and 
(iii) striated for $b = 0$.

@@

First, we must simplify the
form of the free energy \eqref{eq:free_energy}
using integration by parts and \eqref{eq:SL}
to obtain
\begin{equation}
\label{eq:free_energy2}
F = -\gamma
\int_{\Gamma} \rho g \nabla u \cdot \nnu \,\dif s
+ \frac{M}{2}
\sum_{j \neq i} 
P\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right).
\end{equation}
%
Here, we have substituted $g$ for $u$ since the boundary values are given.
However, evaluating $\nabla u \cdot \nnu$ on $\Gamma$ based on \eqref{eq:SL_BIE}
involves calculating a quadruple layer potential which has a
well-known obstacle in numerical implementation.
To overcome this obstacle, we use
%
\begin{equation}
\label{eq:normal_deriv}
\nabla u(\xx) \cdot \nnu(\xx)=
%\frac{\partial}{\partial \nnu_\xx} \DD[\sigma](\xx) =
-\frac{1}{\rho^2} {\bf t}_\xx\cdot \SSS[\sigma{\bf t}](\xx)
+ \frac{\dif}{\dif s}\SSS\left[\frac{\dif \sigma}{\dif s}\right](\xx), \quad \xx \in \Gamma.
\end{equation}
%
Here, ${\bf t}(\xx)$ is the tangent vector and $\dif/\dif s$ is the arclength derivative.
See the Appendix section \ref{sec:appendix} for the proof and details.
Substituting \eqref{eq:normal_deriv} into \eqref{eq:free_energy2} for the normal derivative
leads to single layer integral which is more straightforward to evaluate and we compute the
arclength derivative using spectrally accurate Fourier transform.
We have validated the form of \eqref{eq:normal_deriv} by extrapolating 
the primal energy \eqref{eq:free_energy} along test curves placed slightly
outside the particles.

Figure~\ref{fig:relax_energy}(a) tracks the free energy profiles for all relaxation runs.
For the 198-particle cases, we normalized the energies by 60/198 and the results
show that all energies decrease with good agreements in all boundary conditions (dashed curves).
This can be considered as evidence that the free energy per particle with specified
boundary condtions is independent of number of particles.

>>>>

The boundary condition on JP can be classified into three categories: min$(g) >0$, min$(g) =0$, and min$(g) <0$. Without loss of generality, 
these three categories correspond to three characteristic values of $b$ in \eqref{eq:bc-type}: $b=2$, $b=1$ and $b=0$, respectively. 
%
To see the effect of the shift parameter $b$, we simulate the dynamics of
198 particles and 60 particles in a quiescent flow as shown in Figure~\ref{fig:relax}.
Three distinct configurations emerge:
(i) bilayers for $b = 1$, 
(ii) multilamellar for $b = 2$, and 
(iii) striated for $b = 0$.

@@

First, we must simplify the
form of the free energy \eqref{eq:free_energy}
using integration by parts and \eqref{eq:SL}
to obtain
\begin{equation}
\label{eq:free_energy2}
F = -\gamma
\int_{\Gamma} \rho g \nabla u \cdot \nnu \,\dif s
+ \frac{M}{2}
\sum_{j \neq i} 
P\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right).
\end{equation}
%
Here, we have substituted $g$ for $u$ since the boundary values are given.
However, evaluating $\nabla u \cdot \nnu$ on $\Gamma$ based on \eqref{eq:SL_BIE}
involves calculating a quadruple layer potential which has a
well-known obstacle in numerical implementation.
To overcome this obstacle, we use
%
\begin{equation}
\label{eq:normal_deriv}
\nabla u(\xx) \cdot \nnu(\xx)=
%\frac{\partial}{\partial \nnu_\xx} \DD[\sigma](\xx) =
-\frac{1}{\rho^2} {\bf t}_\xx\cdot \SSS[\sigma{\bf t}](\xx)
+ \frac{\dif}{\dif s}\SSS\left[\frac{\dif \sigma}{\dif s}\right](\xx), \quad \xx \in \Gamma.
\end{equation}
%
Here, ${\bf t}(\xx)$ is the tangent vector and $\dif/\dif s$ is the arclength derivative.
See Appendix in \S\ref{sec:appendix} for the proof and details.
Substituting \eqref{eq:normal_deriv} into \eqref{eq:free_energy2} for the normal derivative
leads to single layer integral which is more straightforward to evaluate and we compute the
arclength derivative using spectrally accurate Fourier transform.
We have validated the form of \eqref{eq:normal_deriv} by extrapolating 
the primal energy \eqref{eq:free_energy} along test curves placed slightly
outside the particles.

Figure~\ref{fig:relax_energy}(a) tracks the free energy profiles for all relaxation runs.
For the 198-particle cases, we normalized the energies by 60/198 and the results
show that all energies decrease with good agreements in all boundary conditions (dashed curves).
This can be considered as evidence that the free energy per particle with specified
boundary condtions is independent of the total particle number $(N_b)$.
